---
title: "M5 Forecasting Dataset Overview"
output: html_notebook
---
## package import
```{r}
library(readr)
library(fpp2)
library(plyr)
```

## Calendar Data
```{r}
calendar <- read_csv("data/calendar.csv")
head(calendar)
```
## Sales Data
```{r}
sell_prices <- read_csv("data/sell_prices.csv")
head(sell_prices)
```
### Summary of sales data
```{r}
summary(sell_prices)
```
## All Time Series Avaliable in dataset
1. Unit sales of all products, aggregated for all stores/states - 1
2. Unit sales of all products, aggregated for each State - 3
3. Unit sales of all products, aggregated for each store - 10
4. Unit sales of all products, aggregated for each category - 3
5. Unit sales of all products, aggregated for each department - 7
6. Unit sales of all products, aggregated for each State and category - 9
7. Unit sales of all products, aggregated for each State and department - 21
8. Unit sales of all products, aggregated for each store and category - 30
9. Unit sales of all products, aggregated for each store and department - 70
10. Unit sales of product x, aggregated for all stores/states - 3049
11. Unit sales of product x, aggregated for each State - 9147
12. Unit sales of product x, aggregated for each store - 30490
13. Sales Price of all products, aggregated for all stores/states - 1

## Time Series
```{r}
time_series = NULL
```

### Time Series 13
#### Sales Price of all products, aggregated for all stores/states
how many items are sell per day
```{r}
sell_freq = count(sell_prices$wm_yr_wk)
time_series.13 = ts(sell_freq$freq,
                   start = c(2011, 4),
                   frequency = 52)
plot(time_series.13)
```
## Time Series Data
```{r}
dataset <- read_csv("data/sales_train_validation.csv")
head(dataset)
```
### Time Series 1 - Unit sales of all products, aggregated for all stores/states
```{r}
time_series.1 = ts(
  colSums(dataset[, 7:length(dataset)]),
  start = c(2011, 29),
  frequency = 365
)
plot(time_series.1)
```
#### Time Series 1 - Properties
##### Corelation with event
##### Event Time Series
```{r}
f = function(x) {
  output = 0
  if (!is.na(x[1])){
    output = output + 1
  }
  
  if (!is.na(x[2])){
    output = output + 1
  }
  
  return(output)
}

time_series.events = ts(
  apply(as.matrix(calendar[1:length(time_series.1),c('event_name_1','event_name_2')]), 1, f),
  start = c(2011, 29),
  frequency = 365
)
autoplot(time_series.events)
```
#### Relationship between events and time series 1
##### simple plot
```{r}
time_series.1_events = ts.union(time_series.1, time_series.events)
autoplot(time_series.1_events, facets=TRUE)
```
##### qplot
```{r}
qplot(time_series.1, time_series.events, data=as.data.frame(time_series.1_events))
```
#### SNAP
```{r}
time_series.snaps = ts(
  calendar[1:length(time_series.1),c('snap_TX','snap_WI', 'snap_CA')],
  start = c(2011, 29),
  frequency = 365
)
autoplot(time_series.events)
```
#### Relationship between snaps and time series 1
##### simple plot
```{r}
time_series.1_snaps = ts.union(time_series.1, time_series.snaps)
autoplot(time_series.1_snaps, facets=TRUE)
```
#### Relationship between snap and time series 1
```{r}
GGally::ggpairs(as.data.frame(time_series.1_snaps))
```
```{r}
GGally::ggpairs(as.data.frame(time_series.1_events))
```
##### lag plot of time series 1
```{r}
gglagplot(window(time_series.1, start = 2011))
```
##### Autocorelation plot of time series 1
```{r}
ggAcf(time_series.1)
```
##### conclusion of autocorelation plot for time series 1
time series 1 have trend and seasonality both.





































